Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-06-19 Paper/main.tex
Updated figs and tables

%#include
\begin{table}[H]
    \caption{Summary statistics table}
    \label{Sum_Stats}
    \begin{center}
       \scriptsize{\input{./Tables/SS_bylawyer.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Summary stats of outcomes, basic and strategic variables by type of (employee's) lawyer.
    \textit{Do file: } \texttt{Table\_SS\_bylawyer.do}
\end{table}

%#include
\begin{table}[H]
    \caption{Baseline Expectations}
    \label{Table_expectations}
    \begin{center}
       \scriptsize{\input{./Tables/SS_A.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes:} 
    Summary statistics of parties' beliefs. We show mean and standard deviation for the whole sample, \& dividing by type of employee's lawyer.
    \textit{Do file: } \texttt{Table\_SS.do  Table\_SS\_bylawyer.do}
\end{table}

@@

%#include
\begin{table}[H]
    \caption{Treatment Efects by Month}
    \label{Table_effects_F}
    \begin{center}
    \scriptsize{\input{./Tables/Minicortes_2_PA.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{mini\_cortes\_2.do}
\end{table}

@@

@@

\begin{figure}[H]
    \caption{Conciliation over time}
    \label{Figure_dynamicsConciliation}
    \begin{center}
        \includegraphics[width=0.7\textwidth]{con_overtime.pdf}
        \end{center}
        {\footnotesize \textit{Notes: } Conciliation over time in HD database and pilot database.}
        {\footnotesize \textit{Do file: } \texttt{con\_overtime.do}}
\end{figure}

@@

\begin{table}[H]
    \caption{Summary statistics table }
    \label{tab:SS}
    \begin{center}
        \tiny{\input{./Tables/SS.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
Summary stats of outcomes, basic and strategic variables
    \textit{Do file: } \texttt{Table\_SS.do}
\end{table}

@@

%#appendix
\begin{table}[H]
    \caption{Treatment Effects by Month (including basic variables controls)}
    \label{Table_effects}
    \begin{center}
    \scriptsize{\input{./Tables/Minicortes_2_B_PA.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{mini\_cortes\_2\_B.do}
\end{table}

>>>>

%#include
\begin{table}[H]
    \caption{Summary statistics table }
    \label{tab:SS}
    \begin{center}
        \tiny{\input{./Tables/SS.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
Summary stats of outcomes, basic and strategic variables
    \textit{Do file: } \texttt{Table\_SS.do}
\end{table}

\begin{table}[H]
    \caption{Summary statistics table by end mode }
    \label{tab:SS}
    \begin{center}
        \tiny{\input{./Tables/SS_bymodotermino.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
Summary stats of outcomes, basic and strategic variables by end mode.
    \textit{Do file: } \texttt{Table\_SS\_bymodotermino.do}
\end{table}

@@

%#include
\begin{table}[H]
    \caption{Treatment Effects by months after treatment}
    \label{Table_effects_F}
    \begin{center}
    \scriptsize{\input{./Tables/minicortes_monthstreatment.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{minicortes\_monthstreatment.do}
\end{table}

% \begin{table}[H]
%     \caption{Treatment Efects by Month}
%     \label{Table_effects_F}
%     \begin{center}
%     \scriptsize{\input{./Tables/Minicortes_2_PA.tex}}
%     \end{center}
%     \footnotesize
%     \textit{Notes:} 
%     Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
%     \textit{Do file: } \texttt{mini\_cortes\_2.do}
% \end{table}

@@

\begin{figure}[H]
    \centering
    \includegraphics{covariates_categorical.png}
    \caption{Covariate distribution for Pilot and Historical Data: continuous variables}
    \label{covariates_categorical}
\end{figure}

\begin{figure}[H]
\caption{Covariate distribution in Historical and Pilot data}
\label{covariate_distribution}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Continuous variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_continous.png}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Categorical variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_categorical.png}
        \end{subfigure}
    \end{center}
\end{figure}

@@

\begin{figure}[H]
    \caption{Conciliation over time}
    \label{Figure_dynamicsConciliation}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=1\textwidth]{con_overtime.pdf}
     \end{subfigure}
        \begin{subfigure}{0.49\textwidth}    
         \centering
        \includegraphics[width=1\textwidth]{beta_monthsafter.pdf}
     \end{subfigure}
        \end{center}
        {\footnotesize \textit{Notes: } Conciliation over time in HD database and pilot database. Figure on the left shows the effect of conciliation on treated against control for different months after initial sue.}
        {\footnotesize \textit{Do file: } \texttt{con\_overtime.do , beta\_monthsafter.do}}
\end{figure}

@@

\begin{table}[H]
    \caption{Baseline Expectations}
    \label{Table_expectations}
    \begin{center}
       \scriptsize{\input{./Tables/SS_A.tex}}
    \end{center}
    \footnotesize    
    \textit{Notes:} 
    Summary statistics of parties' beliefs. We show mean and standard deviation for the whole sample, \& dividing by type of employee's lawyer.
    \textit{Do file: } \texttt{Table\_SS.do  Table\_SS\_bylawyer.do}
\end{table}

@@

%#appendix
\begin{table}[H]
    \caption{Treatment Effects by months after treatment (including basic variables controls)}
    \label{Table_effects}
    \begin{center}
    \scriptsize{\input{./Tables/minicortes_monthstreatment_B.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
    Calc=Conc and Calc=Conc=0 shows the p-value for the respective tests.
    \textit{Do file: } \texttt{minicortes\_monthstreatment.do}
\end{table}
